\documentclass[a4paper, 12pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{babel}
\usepackage[raggedright]{titlesec}
\usepackage{blindtext}
\titleformat{\paragraph}[hang]{\normalfont\normalsize\bfseries}{\theparagraph}{1em}{}
\titlespacing*{\paragraph}{0pt}{3.25ex plus 1ex minus .2ex}{0.5em}
\setcounter{section}{0}
\begin{document}
\section*{Indexicals}
\paragraph{Definition Of An Indexical}
According to the Oxford Dictionary, an indexical is ``a word or expression whose meaning is dependent on the context in which it is used (such as here, you, me, that one there, or next Tuesday)''. For example, the noun ``tomorrow'' is an indexical because its meaning depends on today's date. If you picked up a piece of a paper from the ground that said ``tomorrow is my birthday'', this sentence would make no sense because there is no way to determine what ``tomorrow'' refers to. This would be an example of a hanging indexical.
\paragraph{Indexicals Are Everywhere}
Although ``tomorrow'', ``now'', and ``you'' are all examples of indexicals, they are rarely meaningless because when we speak of these words, we generally understand what they refer to. However, we often communicate with indexicals that have no meaning. For example, the phrase ``whatever you do is wrong'' has no meaning because the speaker has not determined what ``whatever you do'' refers to. Furthermore, the phrase ``I don't have what they have'' has no meaning because the speaker has not determined what ``they have'' refer to. You will begin to see that hanging indexicals are everywhere in our language because these words appear to describe something of the world when in actually they do not.
\paragraph{Hanging Indexicals Do Not Exist}
Because indexicals are references to things of the world, they themselves do not exist in the sense that they do not describe anything of reality. For example, the concept of ``tomorrow'' does not exist if we have not determined what exactly ``tomorrow'' refers to. However, a particular ``tomorrow'' such as January 1st 2019 does exist because it refers to a state of the world when a clock turns midnight on that date.
\end{document}
